|

### 2023-05-19 manuscript/paper.Rmd
Some updates.

More specifically, @Woltring2018 mentions six eras of modern baseball": 
"Baseball has endured much change over the course of its history, and because of constant change, the modern era of baseball has been segmented into six distinct sub-eras. A common list presented at Baseball-Reference described the eras as the Dead Ball Era (1901-1919), the Live Ball Era (1920-1941), the Integration Era (1942-1960), the Expansion Era (1961-1976), the Free Agency Era (1977-1993) and the Long Ball/Steroid Era (1994-2005) (17)."  @Woltring2018 notes that they name a seventh era after 2006, which they term the Post Steroid Era.

@@

@LeeFort2005 looks for structural changes in competitive balance of the two league American and National.  Use methods from Andrews1993, Bai1997, 1999 and Bai and Perron 1998 and 2003 to look for break points between 1901 -1999.  Theuy measure competitive balance in two ways: 1) Noll 1988 and Scully 1989 and 2) Lee (2004). They find break point sin competitive balance in 1912, 1926, and 1933 for the NL and in 1926 and 1957 in the AL.

@@

>>>>

More specifically, @Woltring2018 mentions six eras of modern baseball": 
"Baseball has endured much change over the course of its history, and because of constant change, the modern era of baseball has been segmented into six distinct sub-eras. A common list presented at Baseball-Reference described the eras as the Dead Ball Era (1901-1919), the Live Ball Era (1920-1941), the Integration Era (1942-1960), the Expansion Era (1961-1976), the Free Agency Era (1977-1993) and the Long Ball/Steroid Era (1994-2005)."  @Woltring2018 notes that they name a seventh era after 2006, which they term the Post Steroid Era.

@@

@LeeFort2005 looks for structural changes in competitive balance of the two league American and National.  Use methods from Andrews1993, Bai1997, 1999 and Bai and Perron 1998 and 2003 to look for break points between 1901 -1999.  Theuy measure competitive balance in two ways: 1) @Noll1988 and @Scully1989 and 2) Lee 2004. They find break point sin competitive balance in 1912, 1926, and 1933 for the NL and in 1926 and 1957 in the AL.

@@

<!-- https://journals.sagepub.com/doi/10.1177/152700250100200204 -->
